Issues with Dynamical Measurements Across the Disk

### 2019-02-20 paper/ms.tex

\subsection{Quantification of the effect of systematic coordinate-system
errors} \label{ssec:quant} First, we illustrate the phase-dependence of an
example systematic error in the Galactocentric coordinate system. We will
consider three orbits in the model potential described in
Section~\ref{ssec:action_comp} that are typical of stars in the stellar thin
disk, stellar thick disk, and the stellar halo. We summarize their initial
positions in phase space and the actions computed by integrating their orbits
in the correct potential in Table~\ref{tab:orbits}. Each orbit, integrated
without systematic coordinate errors, is plotted in Appendix~\ref{app:orbits}.
We will refer to these orbits by their names (thin-disk, thick-disk, halo)
henceforth.

>>>>

\subsection{Quantification of the effect of systematic coordinate-system
errors} \label{ssec:quant}
First, we illustrate the phase-dependence induced by an
example systematic error in the Galactocentric coordinate system. We will
consider three orbits in the model potential described in
Section~\ref{ssec:action_comp} that are typical of stars in the stellar thin
disk, stellar thick disk, and the stellar halo. We summarize their initial
positions in phase space and the actions computed by integrating their orbits
in the correct potential in Table~\ref{tab:orbits}. Each orbit, integrated
without systematic coordinate errors, is plotted in Appendix~\ref{app:orbits}.
We will refer to these orbits by their names (thin-disk, thick-disk, halo)
henceforth.
